Areal kernel demonstration

### 2022-10-27 src/0_demo_areal-kernels/areal-kernels.Rmd
Improve areal-kernels

---
title: "Areal kernel demonstration"
author: "Adam Howes"
output: html_document
---

@@

```{r}
sf <- mw

# The number of integration points within each area
L <- 10

# The method for selecting integration points
type <- "hexagonal"

# The number of areas
n <- nrow(sf)

# Draw L samples from each area according to method type
samples <- sf::st_sample(sf, type = type, size = rep(L, n))

@@

plot_samples(samples)

# Construct an (L * n) * (L * n) matrix containing the Euclidean distance between each sample
# Note that this ^ will not be exact for some settings of type (hexagonal, regular)
S <- sf::st_distance(samples, samples)
dim(S)

# Data structure for unequal number of points in each area
sample_index <- sf::st_intersects(sf, samples)
sample_lengths <- lengths(sample_index)
start_index <- sapply(sample_index, function(x) x[1])

@@

>>>>

---
title: "Areal kernel demonstration"
author:
- name: Adam Howes
output:
  html_document:
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    df_print: paged
    code_folding: show
    theme: lumen
abstract: |
  **Task** We briefly demonstrate the fitting of areal kernel models in Stan.
---

@@

```{r}
sf <- mw
```

The number of integration points within each area:

```{r}
L <- 10
```

The method for selecting integration points:

```{r}
type <- "hexagonal"
```

The number of areas:

```{r}
n <- nrow(sf)
```

Draw $L$ samples from each area according to method type:

```{r}
samples <- sf::st_sample(sf, type = type, size = rep(L, n))

@@

plot_samples(samples)
```

Construct an $nL \times nL$ matrix containing the Euclidean distance between each sample.
Note that this the $L$ actually obtained will not be exact for some settings of type (`hexagonal`, `regular`):

```{r}
S <- sf::st_distance(samples, samples)
dim(S)
```

Data structure for unequal number of points in each area:

```{r}
sample_index <- sf::st_intersects(sf, samples)
sample_lengths <- lengths(sample_index)
start_index <- sapply(sample_index, function(x) x[1])

@@

# Stan code

## `centroid.stan`

```{cpp, echo=TRUE, eval=FALSE, output.var="ex", code=readLines('centroid.stan')}
```

## `integrated.stan`

```{cpp, echo=TRUE, eval=FALSE, output.var="ex", code=readLines('integrated.stan')}
```

# Original computing environment

```{r}
sessionInfo()
```
